% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{Title Goes Here}
\subtitle{[Extended Abstract]}

\numberofauthors{4} 
\author{
\alignauthor
Brian Clee\\
       %\affaddr{NC State University}\\
       %\affaddr{Address One}\\
       \email{bpclee@ncsu.edu}
\alignauthor
Effat Farhana\\
       %\affaddr{NC State University}\\
       %\affaddr{Address Two}\\
       \email{efarhan@ncsu.edu}
\and % go to new row
\alignauthor
Arjun Madan\\
       %\affaddr{NC State University}\\
       %\affaddr{Address Three}\\
       \email{amadan2@ncsu.edu}
\alignauthor
Ran Tan\\
       %\affaddr{NC State University}\\
       %\affaddr{Address Four}\\
       \email{rtan2@ncsu.edu}
}

\date{1 February 2016}


\maketitle
\begin{abstract}
Abstract text. 
\end{abstract}

%see http://www.acm.org/sigs/publications/sigguide-v2.2sp section 2.3.2
% A category with the (minimum) three required fields
\category{D.2.2}{Software Engineering}{Design Tools and Techniques}[Modules and interfaces, programmer workbench, user interfaces]
%A category including the fourth, optional field follows...
\category{D.2.3}{Software Engineering}{Coding Tools and Techniques}[Program Editors]

% see http://www.acm.org/sigs/publications/sigguide-v2.2sp section 2.3.3
\terms{Human Factors, Management, Performance, Theory}

\keywords{Code cloning, code duplication, copy and pasting, eclipse plug-ins, programmer habits, programmer productivity}

\section{Introduction}
Brian!

Citation of Einstein paper~\cite{Einstein}.

\section{Project Goals}
Effat!
PUTG
Project features
\\
1. Multi-item\\
2. System Wide copy\\
3. Context Awareness\\
    a. How do we display items?\\
    b. How do we order the items?\\
4. Code Cloning   \\
5. Design Pattern detection\\ 
6. Touch screen interactions\\

\section{User Patterns and Behavior}
Brian!
Why do we need to copy/paste
Studies that show we copy/paste a lot

\section{Copy and Paste in Practice}
Arjun!
Default clipboard, between windows, studies on copy and pasting with stats, current existing solutions.

\section{Code Cloning and Pattern Detection}
Ran!
Theoretical section on code cloning and pattern detection and management.

\section{Conclusion}
Arjun!
Refresh on our main points and themes. Talk about our 3/4 features we will be doing.

\bibliographystyle{abbrv}
\bibliography{sample}

%\balancecolumns 

\end{document}
